\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates on progress

\medskip
Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields. \citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number ($N_{c}$) as this is defined below in eq.~\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell,
T is the surface tension and U is a velocity characteristic of the moving interface.

>>>>

\medskip
Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields. \citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number ($N_{c}$) as this is defined below in eq.~\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell, $ \alpha \beta \gamma $ is the surface tension and U is a velocity characteristic of the moving interface.
